Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2016-02-01 document/ms.tex
checking my monte carlo skills

@@

>>>>

\newcommand{\params}{{\ensuremath{\bvec{w}}}}
\newcommand{\poppars}{{\ensuremath{\theta}}}

@@

\section{The occurrence rate of long-period exoplanets}

Geometric:

\begin{eqnarray}
Q_{\mathrm{geom},k} (\params) &=& \frac{R_{\star,k}}{a_k(\params)} \\
&=& \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,P^{-2/3}
\end{eqnarray}

Temporal:

\begin{eqnarray}
Q_{\mathrm{temp},k} (\params) &=& \frac{T_k}{P}
\end{eqnarray}
where $T_k$ is the total observing baseline for target $k$.
Combined with the detection efficiency $Q_{\mathrm{det}}(\params)$ (assumed to
be constant for each target), the total completeness as a function of the
parameters is
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{temp},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \\
&=& Q_{\mathrm{det},k}(\params) \,
    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,
    R_{\star,k}\,T_k\,P^{-5/3} \quad.
\end{eqnarray}

The likelihood function for the catalog of planet candidates is
\begin{eqnarray}
p(\{\params_n\}\,|\,\poppars) &\propto&
    \exp \left(
        \int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\params
    \right) \, \prod_{n=1}^N f_\poppars (\params_n) \quad.
\end{eqnarray}

Therefore
\begin{eqnarray}
\int f_\poppars (\params)\,\sum_{k=1}^K Q_k(\params) \dd\ln P\dd\ln R &=&
    \bar{Q}\,\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}
        \dd\ln P\dd\ln R
\end{eqnarray}
where
\begin{eqnarray}
\bar{Q} &=& \sum_{k=1}^K
    \left[\frac{4\,\pi^2}{G\,M_{\star,k}}\right]^{1/3}\,R_{\star,k}\,T_k
\quad.
\end{eqnarray}

The easiest way to evaluate this integral in practice is to use Monte Carlo
integration to find
\begin{eqnarray}
\int Q_{\mathrm{det}}(\params)\,f_\poppars(\params)\,P^{-5/3}\dd\ln P\dd\ln R
&=& \frac{F}{J}\sum_{j=1}^J Q_{\mathrm{det}}(P^{(j)},\,R^{(j)})\,
        f_\poppars(P^{(j)},\,R^{(j)})
\end{eqnarray}
where
\begin{eqnarray}
F &=& \frac{3}{5}\,[P_\mathrm{min}^{-5/3}-P_\mathrm{max}^{-5/3}]\,
      [\ln R_\mathrm{max} - \ln R_\mathrm{min}]
\end{eqnarray}
and
\begin{eqnarray}
P^{(j)} \sim P^{-8/3} &\mathrm{and}&
\ln R^{(j)} \sim \mathcal{U}(\ln R_\mathrm{min},\,\ln R_\mathrm{max})
\end{eqnarray}

\begin{eqnarray}
f_\poppars (\params) &=& \frac{1}{f_0}\,C\,P^\alpha\,R^\beta
\end{eqnarray}
where
\begin{eqnarray}
f_0 &=&
    \int_{P_\mathrm{min}}^{P_\mathrm{max}}
    \int_{R_\mathrm{min}}^{R_\mathrm{max}}
    P^\alpha\,R^\beta\dd\ln P\dd\ln R
\end{eqnarray}
